Wrinkling and yielding of protein gel

### 2013-09-09 poster_Rome.tex
parabolic fit of tz speckle decodehence
Link wrinkles -> fractures

\begin{textblock}{15}(0,8)
	\Head{Kinetic by transmission macroscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	33 min & 38 min & 43 min & 48 min & 1h & 1h15 & 2h30\\
	\includegraphics[width=2\TPHorizModule]{prise_0100_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0130_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0160_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0190_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0250_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0360_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0799_resized.jpg}\\
	\end{tabular*}
\end{textblock}

\begin{textblock}{3}(0,10)
	\Subhead{Length scales}
	\begin{itemize}
	\item A fundamental that does not evolve
	\item Nested structures as ``harmonics''
	\end{itemize}
	\Subhead{Qualitatively different from}
	\begin{itemize}
	\item phase separation patterns 
	\item Turing patterns
	\item usual wrinkles
	\end{itemize}	 
\end{textblock}

@@

\begin{textblock}{4}(11,11)
	\addvspace{2em}
	\Subhead{Volume}

@@

\begin{textblock}{15}(0,14)
	\Head{Kinetic by confocal microscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}\\
\end{tabular*}
\end{textblock}

@@

\begin{textblock}{4}(5,16)
	\Head{Creep and fractures}
	Couette cell, no brush, the gel sticks

	\begin{tikzpicture}
	\begin{loglogaxis}[%
		name=a,
		xlabel={$t\,(s)$},
		ylabel={Shear rate $(s^{-1})$},
		]
		\addplot+[no marks, Accent2] file {Y34_strain_rate_log.txt};
		\draw[<->] (axis cs:1e-1,1) -- (axis cs:1.3e3,5e-4) node[midway,above,rotate=-21] {Andrade};
		\node at (axis cs:1.3e3,1e-4) (det){};
		\node at (axis cs:2.3e3,1e4) (touch){};
	\end{loglogaxis}
	\draw[<-, Accent1, ultra thick] (det) -- ++(0,-4em) node[left] {Fractures appear};
	\draw[<-, Accent1, ultra thick] (touch) -- ++(0,3em) node[left] {Fractures meet};
	\end{tikzpicture}\hfill
	\begin{tikzpicture}[inner sep=0]
		\node[above right] at (0,1em) {\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_avant_div.jpg}};
		\node[below right] (b){\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_premiere_frac.jpg}};
		\node[below left=0 of b.north east]{\includegraphics[width=0.75\TPHorizModule]{detail_premiere_frac.jpg}};
		\draw[Accent2,radius=0.07\TPHorizModule] ++(b.north east) +(-1.14\TPHorizModule,-1.05\TPHorizModule) circle;
		\draw[Accent2,radius=0.09\TPHorizModule] ++(b.north east) +(-0.435\TPHorizModule,-0.375\TPHorizModule) circle;
	\end{tikzpicture}
\end{textblock}

\begin{textblock}{5}(10,16)
	\Head{Ultrasound speckles}
	\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group size=2 by 1, 
			horizontal sep=\TPHorizModule,
		},
		width=2\TPHorizModule,
		xmin=0,xmax=200,
		xlabel={t},
		axis on top,
		xtick={28, 100, 172},
		xticklabels={49h30, 50h, 50h30},
		]
		\nextgroupplot[ymin=0, ymax=32,	ylabel={$z (\si{\milli\metre})$}, title={$r=\SI{200}{\micro\metre}$}]
		\addplot graphics[
			xmin=0,xmax=200,
			ymin=0,ymax=32,
			]{Y137_speckleBF_tz.png};
		\plot[no marks,Accent2]  {32-1/(x-187)};
		\draw[Accent1] (axis cs:187,0)--(axis cs:187,32);

		\nextgroupplot[ymin=0, ymax=2,	ylabel={$r (\si{\milli\metre})$}, title={$z=\SI{8}{\milli\metre}$}]
		\addplot graphics[
			xmin=0,xmax=200,
			ymin=0,ymax=2,
			]{Y137_speckleBF_tr.png};
			\draw[Accent2] (axis cs:172,0)--(axis cs:172,2) node[pos=0.66, left, font=\small] {detach from the rotor};
			\draw[Accent1] (axis cs:187,0)--(axis cs:187,2) node[pos=0.33, left, font=\small] {global yield};
	\end{groupplot}
	%\draw[<-,Accent2, very thick] (decol) -- +(0,1em);
	%\draw[<-,Accent1, very thick] (casse) -- +(0,1em);
	\end{tikzpicture}
\end{textblock}

\textblockcolour{lightgray!50!white}
\TPMargin*{ 0.125\TPHorizModule }
\begin{textblock}{2.875}(12,2.625)%real width of 3
	\Head{Take away}
	\Subhead{A new kind of pattern}
	\begin{itemize}
		\item nested
		\item self generated
		\item boundary conditions
	\end{itemize}
	\Subhead{A link with fractures}
\end{textblock}%Conclusion

>>>>

\begin{textblock}{15}(0,8)
	\Head{Pattern kinetics by transmission macroscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	33 min & 38 min & 43 min & 48 min & 1h & 1h15 & 2h30\\
	\includegraphics[width=2\TPHorizModule]{prise_0100_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0130_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0160_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0190_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0250_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0360_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0799_resized.jpg}\\
	\end{tabular*}
\end{textblock}

\begin{textblock}{3}(0,10)
	Corresponds with the fall of $G^\prime$.

	\Subhead{Length scales}
	\begin{itemize}
	\item A fundamental that does not evolve
	\item Nested structures as ``harmonics''
	\end{itemize}
	\Subhead{Qualitatively different from}
	\begin{itemize}
	\item phase separation patterns 
	\item Turing patterns
	\item usual wrinkles
	\end{itemize}	 
\end{textblock}

@@

\begin{textblock}{4}(11,11)
	\addvspace{2em}
	\Subhead{Synæresis and swelling}

@@

\begin{textblock}{15}(0,14)
	\Head{Wrinkling kinetics by confocal microscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}\\
\end{tabular*}
\end{textblock}

@@

\begin{textblock}{4}(5,16)
	\Head{Creep and fractures}
	Couette cell, no brush, the gel sticks, no pattern.\\
	Wait \SI{8}{\hour} for equilibration, then apply constant stress.

	\begin{tikzpicture}
	\begin{loglogaxis}[%
		name=a,
		xlabel={$t\,(s)$},
		ylabel={Shear rate $(s^{-1})$},
		]
		\addplot+[no marks, Accent2] file {Y34_strain_rate_log.txt};
		\draw[<->] (axis cs:1e-1,1) -- (axis cs:1.3e3,5e-4) node[midway,above,rotate=-21] {Andrade};
		\node at (axis cs:1.3e3,1e-4) (det){};
		\node at (axis cs:2.3e3,1e4) (touch){};
	\end{loglogaxis}
	\draw[<-, Accent1, ultra thick] (det) -- ++(0,-4em) node[left] {Fractures appear};
	\draw[<-, Accent1, ultra thick] (touch) -- ++(0,3em) node[left] {Fractures meet};
	\end{tikzpicture}\hfill
	\begin{tikzpicture}[inner sep=0]
		\node[above right] at (0,1em) {\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_avant_div.jpg}};
		\node[below right] (b){\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_premiere_frac.jpg}};
		\node[below left=0 of b.north east]{\includegraphics[width=0.75\TPHorizModule]{detail_premiere_frac.jpg}};
		\draw[Accent2,radius=0.07\TPHorizModule] ++(b.north east) +(-1.14\TPHorizModule,-1.05\TPHorizModule) circle;
		\draw[Accent2,radius=0.09\TPHorizModule] ++(b.north east) +(-0.435\TPHorizModule,-0.375\TPHorizModule) circle;
	\end{tikzpicture}

	\begin{tabular}{b{0.55\textwidth}b{0.45\textwidth}}
	\begin{tikzpicture}
	\begin{loglogaxis}[%
		ylabel={Breaking time (s)},ylabel near ticks,
		xlabel={Stress $\sigma$ (Pa)},
		xmin=10,
		legend style={font=\small\sc}, legend pos=south west,
		mark size={0.2em},
		]
		\addplot+[only marks, Accent1, mark options={fill=Accent1}] coordinates {(40, 67225) (50,29860) (100,398) (200,4)};
		\addplot+[only marks, Accent2, mark options={fill=Accent2}] table[x index=0, y index=1]{cas4_GDL1_t_cassure_sigma.txt};
		\legend{gdl 4\%, gdl 1\%};
		\addplot+[Accent1, no marks, forget plot, domain=40:200] gnuplot {6.32e+14*x^{-6.14}};
		\addplot+[Accent2, no marks, forget plot, domain=150:1000] gnuplot {3.93e+17*x^{-5.44}};
	\end{loglogaxis}
	\end{tikzpicture}&
	Irreversible fractures\linebreak
	\Subhead{Fracture\linebreak wavelength}
	\begin{itemize}
		\item stress-independent
		\item composition-indep.
		\item $\propto$ gap
	\end{itemize}\\
	\end{tabular}

	\begin{tikzpicture}
	\begin{axis}[%
		width=0.95\textwidth,
		height=0.4\textwidth,
		xmin=0,xmax=3.5,xlabel={gap (\si{\milli\metre})},
		xtick={0, 0.5,...,3},
		ymin=0,ylabel={$\lambda$ (\si{\milli\metre})},
		xlabel near ticks,
		ylabel near ticks,
		%mark size={0.01\textwidth},
		legend cell align=left,
		legend style={font=\small}, legend pos=north west,
		]
		\addplot+[%
			only marks, Accent1, mark options={fill=Accent1},
			error bars/.cd,
			y dir=both,y explicit,
			x dir=none,x fixed=0.05,
			]
			coordinates {
				(0.5,0.6) +-(0,0.12)
				(1, 1.33) +-(0,0.14)
				(1.5,1.5) +-(0,0.14)
				(1.5, 1.25) +- (0,0.77)
				(3,3.75) +- (0,0.4)
				(3, 4.2) +-(0,0.4)};
		\addplot+[%
			only marks, Main, mark options={fill=Main},
			error bars/.cd,
			y dir=both,y explicit,
			x dir=none,x fixed=0.05,
			]
			coordinates
			{(2.5,3.2) +- (0,0.84)};
		\addplot+[%
			only marks, Accent2, mark options={fill=Accent2}, mark=triangle,
			error bars/.cd,
			y dir=both,y explicit,
			x dir=none,x fixed=0.05,
			]
			coordinates
			{(2,2.29) +- (0,0.13)};
		\legend{$R_\text{out}=\SI{25}{\milli\metre}$, $R_\text{out}=\SI{37.5}{\milli\metre}$, $R_\text{out}=\SI{40}{\milli\metre}$};
		\addplot+[domain=0:3.5, no marks, Accent1, forget plot] {1.25*x};
	\end{axis}
	\end{tikzpicture}
\end{textblock}

\begin{textblock}{5}(10,16)
	\Head{Ultrasound speckles}
	\Subhead{Probe deformation inside the gap}

	\begin{tikzpicture}[ultra thick, font=\small]
	\node[above right, inner sep=0] (sch) {\includegraphics[width=0.4\textwidth]{usv_3D_image}};
	\draw[<-] (0.3\textwidth,0.11\textwidth) -- +(1em,0) node[right] {water in};
	\draw[->] (0.3\textwidth,0.07\textwidth) -- +(1em,0) node[right] {water out};
	\node[right] at (0.2\textwidth, 0.3\textwidth) (rh) {rheometer};
	\node[above right] at (0.2\textwidth, 0) (arraylabel) {array of transducers};
	\draw[->,dotted]	 (arraylabel.west) -- (0.1\textwidth, 0.1\textwidth);
	\draw[->] (0.06\textwidth, 0.15\textwidth) -- (0,0.15\textwidth) node[draw, left, text width=0.18\textwidth] (mce) {multi-channel electronics};
	\node[above=of mce, draw] (pc) {PC};
	\draw[->] (mce)-- (pc);
	\draw[->] (rh) -- +(0,1em) -| (pc.north);
	\node[below right=1em and 0 of mce.south west, text width=0.18\textwidth] {Gallot et al. RSI (2013).};
	\node[below right =of sch.north east, text width=0.32\textwidth] {3\% of \SI{30}{\micro\metre} acrylamide beads as contrast agent};
	\end{tikzpicture}

	\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=grp,
			group size=2 by 1, 
			horizontal sep=\TPHorizModule,
		},
		width=2\TPHorizModule,
		xmin=0,xmax=200,
		xlabel={t},
		axis on top,
		xtick={28, 100, 172},
		xticklabels={49h30, 50h, 50h30},
		]
		\nextgroupplot[ymin=0, ymax=32,	ylabel={$z (\si{\milli\metre})$}, title={$r=\SI{200}{\micro\metre}$}]
		\addplot graphics[
			xmin=0,xmax=200,
			ymin=0,ymax=32,
			]{Y137_speckleBF_tz.png};
		\addplot[no marks,Accent2, domain=0:32]  ({187-0.272*(x-17.6)^2}, x);
		\draw[Accent1] (axis cs:187,0)--(axis cs:187,32);

		\nextgroupplot[ymin=0, ymax=2,	ylabel={$r (\si{\milli\metre})$}, title={$z=\SI{8}{\milli\metre}$}]
		\addplot graphics[
			xmin=0,xmax=200,
			ymin=0,ymax=2,
			]{Y137_speckleBF_tr.png};
			\draw[Accent2] (axis cs:172,0)--(axis cs:172,2) node[pos=0.66, left, font=\small] {free from the rotor};
			\draw[Accent1] (axis cs:187,0)--(axis cs:187,2) node[pos=0.33, left, font=\small] {global yield};
	\end{groupplot}
	\node[left=of grp c2r1.south west] {rotor};
	\node[left=of grp c2r1.north west] {stator};
	\end{tikzpicture}

	Fractures appear when the gel detaches from the rotor. Creates a free surface that allows synæresis, relaxation of the gelation-induced \linebreak stress and possibly wrinkling.
\end{textblock}

\begin{textblock}{5}(10,22.5)
	\Head{Non equilibrium Creep}
	\Subhead{Fractures need complete overshoot}
	\begin{itemize}
		\item Wait only \SI{40}{\minute}. $G^\prime$ at maximum.
		\item Start creep with $\sigma > \SI{200}{\pascal}$.
		\item[$\Rightarrow$] Break before $G^\prime$ falls.
		\item[$\Rightarrow$] No fracture
	\end{itemize}
\end{textblock}

\textblockcolour{lightgray!50!white}
\TPMargin*{ 0.125\TPHorizModule }
\begin{textblock}{2.875}(12,2.625)%real width of 3
	\Head{Take away}
	\Subhead{A new kind of pattern}
	\begin{itemize}
		\item nested
		\item self generated
		\item boundary conditions
	\end{itemize}
	\Subhead{A good model for solids}
	\begin{itemize}
		\item Andrade creep over 6 decades in time
		\item Irreversible fractures
	\end{itemize}
	\Subhead{A link with fractures}
	\begin{itemize}
		\item Wrinkles can induce plasticity
		\item Wavelengths have the same dependence
		\item Detachment creates a free surface
		\item Fractures need complete overshoot
	\end{itemize}
\end{textblock}%Conclusion
